Scalable Clustering of Genotype Information using MapReduce

### 2015-02-10 doc/publications/journal2014/paper.tex
latest changes

\newcommand{\OnePhaseone}{Phase1\_Chr1}
\newcommand{\NinteenPhaseone}{Phase1\_Chr19}
\newcommand{\SevenPhaseone}{Phase1\_Chr1-7}
\newcommand{\FullPhaseone}{Phase1\_Chr1-22}
\newcommand{\OnePhasethree}{Phase3\_Chr1}
\newcommand{\ThreePhasethree}{Phase3\_Chr1-3}
\newcommand{\FullPhasethree}{Phase3\_Chr1-22}

@@

% COMPARISON TO R
\subsection*{Clustering in Mahout uses less memory than in R}
In this section, we compare the runtime between the k-means clustering implementation in R and Mahout for the small \NinteenPhaseone\ dataset (see Methods). 
We measured the runtime separately for pre-processing stage as well as the clustering stage. 
With Hadoop, pre-processing the data takes approximately 3 minutes, with an allocation of up to 2GB memory per container. The resulting data is stored as a Hadoop 'SequenceFile' of about 835MB in size.
Conversely,  pre-processing the data to R's in-memory matrix takes 56 minutes and uses 17.7GB memory. 
K-means clustering the data, however, is faster with R, using 7s, whereas Mahout takes just over 9 minutes. See Table~\ref{datasetsTime}. \\
Due to the relatively small number of variants, cluster performance is very poor for both methods, with the best Adjusted Rand Index score for clustering individuals in one of 4 populations (see Methods) being 0.730 in Mahout and 0.614 in R (see Table~\ref{datasetsAcc}).

Although the overall Mahout pipeline is about 43 minutes faster than R's, Mahout's k-means clustering takes two orders of magnitude longer. 
This is likely due to the additional overhead involved in spawning the map and reduce processes, and distributing the data between nodes.
R, on the other hand, already has the entire matrix in-memory, on a single machine, this speeds up the clustering significantly as no disk-access or networking is required. However, the amount of memory available on a single machine quickly becomes a limiting factor. 
% DB: very nice but how do you get to the 1.6TB ?
% AO: Fixed
As an example, the entire set of 1000 Genome Project Phase 3 variants would require approximately 1.6TB to be completely loaded into memory as a double-precision matrix (see Table~\ref{datasetsAcc}). This is based on the equation: n*m*8bytes/1GB (where 1GB is 10\^9 bytes). n*m are the matrix dimensions and 8bytes is the memory a double occupies.

% DB: not clear you need to spell out your argument a bit more...
% AO: Fixed
By dividing jobs up into separate 'containers', Hadoop provides great versatility in scaling options. Although in this case, Hadoop has access to 36GB of memory distributed over 3 machines, the size of each container is only 2GB.
Each containers is effectively a self-contained job that is independent from any other container.
Therefore the more resources that the user has available, the more containers that can be run in parallel, decreasing the run-time of the overall job.
This means that our Hadoop job can scale from a single machine with minimal resources (albeit with a longer run-time), to a huge compute cluster with terabytes of RAM.
This benefit of the MapReduce paradigm allows much greater scalability over linear jobs designed in R, for example.

% SCALING UP FEATURES IN MAHOUT
\subsection*{Hadoop scales to genome-wide clustering}
%DB: phase1 full genome ?
%AO: Fixed
In this section we demonstrate Mahout's scaling ability by increasing the numbers of features (variants per sample) input to our algorithm to include the full 79 Million variants from the Phase 3 dataset ( \FullPhasethree\ ).

%DB: Where is the result from \SevenPhaseone\
%AO: Fixed
We tested on various arbitrarily sized datasets to demonstrate the different container sizes required by the pre-processing and clustering, as well as the time required.
On the OnePhaseone dataset, pre-processing takes just under 10 minutes. Clustering took approximately 12 minutes and the container size was the same as with clustering the OnePhasenineteen dataset.
We then increased the input to include the first seven chromosomes. Pre-processing increased to approximately 1 hour and clustering took about 5 hours and 45 minutes.
Our pre-processing algorithm was successful with the same container size as the previous examples, however, we increased both map and reduce container size for the clustering step to 4GB to accommodate the increased vector size.
Finally we used the entire phase one dataset as input. Although pre-processing now takes TIME, it was again successful with the same sized containers as previously.

The significantly increased time required for this larger job is due to the larger container size. With a container size of 6GB, only up to six containers can run simultaneously, as opposed to 24 1.5GB containers.

@@

% SCALING UP SAMPLES IN MAHOUT
\subsection*{Hadoop scales effortless to more than twice the number of samples}
In this section we investigate Mahout's ability to scale with more samples, i.e. the 2504 individuals from the Phase 3 dataset compared to the 1092 individuals in the Phase 1 dataset.
%DB: ok this makes sense from a technical point of view (how fast, memory) but you should not really discuss the accuracy ...
We used the \SevenPhaseone\ and the \ThreePhasethree\ data-sets specifically because they both contain a similar number of variants (19 million).
The container size required for pre-processing the data is identical for both datasets, with the Phase 3 dataset requiring less than double the time of the smaller Phase 1 dataset.
In this case, due to the number of Feature Vectors increasing, rather than the feature size, the memory requirements for k-means clustering should remain similar, as the cluster centres loaded into the containers' memory are approximately the same size.
This proved to be the case, as 4GB allocated per container was the minimum for both datasets. The time to complete clustering was much higher though,
especially due to the fact that only 9 4GB containers can run simultaneously, rather than the 24 1.5GB containers. 
The clustering accuracy is 0.816 for the Phase 1 dataset and 0.xxx for the Phase 3 dataset.

@@

\section*{Conclusion}
In this paper we have applied Mahout's k-means clustering to the task of clustering individuals, based on their genomic variants. 
We provide an interface from VCF format to Hadoop and Mahout, and a toolset to interpret Mahout's clustering output (see Figure 1)
We find that on small datasets the actual clustering stage is two orders of magnitudes slower in Mahout compared to R (9 minutes vs 7 seconds), likely due to the overhead of setting up and co-ordinating the communication between the Hadoop nodes. 
However, increasing either the number of samples or the number of features per sample quickly exceeds the capability of R.
Mahout on the other hand scales effortlessly to more than twice the number samples (2,504) and can process VCF files containing over 79 Million variants per samples.
As the memory required for k-means clustering directly scales with the number of features per sample, we observe that Mahout's implementation
of k-means does not scale to the entire exome dataset, unless memory per container were increased beyond the limits of our cluster.

@@

\begin{methods}
\section{Methods}
\subsection*{Datasets}
We used variant call format (VCF) files from phases 1 and 3 of the 1000 Genomes Project.
Each VCF file details the genetic variation (SNPs and indels) for one chromosome, between each individual and a reference genome derived from GRCh37. 
The phase 1 and phase 3 datasets contain 1,092 and 2,504 individuals, respectively.
Metadata available from the 1000 Genomes Consortium specifies additional attributes for each individual, including population and familial data.\\
We used different subsets of the data for different comparisons. For example, to be able to compare Hadoop with R, we used the VCF file containing chromosome 19 variants (\NinteenPhaseone ).
Then to demonstrate scaling with Hadoop, we use subsets that contain more variants, i.e. \SevenPhaseone\ and \FullPhasethree, which include chromosome 1-7 and the full genome, respectively.
Table~\ref{datasets} contains an overview of the datasets.

\subsection*{Hardware and Software}
We processed the data using a cluster of five VMs on the Microsoft Azure cloud service. Three of the VMs, the 'worker nodes', each have 14GB memory and and 8 CPU cores. These three VMs run the Hadoop2 NodeManager. The NodeManager manages the Yet Another Resource Negotiator (YARN) 'containers'.
The user specifies the memory size of these containers, where map containers can be a different size to reduce containers.
The fourth VM runs the HDFS NameNode, ResourceManager and monitoring services, and the fifth VM, a small, single core machine, runs the Cloudera manager service.
With a total of 42GB memory and 24 CPU cores available between the node managers, we can run 24 YARN containers with 1.5GB memory per container, or 12 YARN containers with 3GB memory per container, in parallel.
Storage consists of a 3TB Hadoop Distributed File System (HDFS) partition distributed across the three worker nodes. Each of these nodes runs a DataNode with a 1TB disk.

@@

We wrote a custom `MapReduce' class in Java to convert VCF files to the aforementioned sequence files. This is scalable and should work on any number of files,
of any file size; limited only by disk space and time. The `map' step creates key value pairs where the primary key is an individual, the secondary key is a variant location, and the value is the variant.
We used a secondary key as this allowed us to implement custom 'collect' and 'sort' classes to process the output of each mapper, based on this secondary key.
This significantly reduced the overall processing time.
The `reduce' step processes the key/value pairs, which were collected by their primary key (individual ID), and sorted by their secondary key (location), and  adds the values (variants) to a sparse array.
The algorithm saves these sparse arrays and keys to disk in the aforementioned SequenceFile format.

@@

The value is zero for independent clusterings and one for identical clusterings. 
We compared the Mahout k-means
clusters and the R k-means clusters to the known clusters based on meta data from the 1000 genome project. For the known clusters,
individuals were partitioned by their super population code (ASN, EUR, AFR, AMR) as well as the 855 families.

\subsection*{Performance}
We collected the job time from the 'Elapsed' time as reported by the Hadoop JobHistory server. This is measured from the job's start time to finish time.
Because k-means clustering performs multiple iterations, and therefore multiple MapReduce jobs, the time we reported is the sum of the elapsed time of each iteration.
For the R job, where we could not easily separate the pre-processing and clustering components, we printed the time between
stages using the function, \texttt{proc.time()}.

@@

\begin{table}[!t]
\processtable{Datasets used in this study.\label{Tab:01}}
{\begin{tabular}{lrrrrr}\toprule
& individuals & variants & in-memory size (GB) & population\\
& & & &groups& \\\midrule
        \NinteenPhaseone & 1,092 & 816,115 & 7.13  & 4\\
        \OnePhaseone & 1,092 & 3,007,196 & 26.27  & 4\\
        \SevenPhaseone & 1,092 & 18,984,880 & 165.85 & 4\\
	\OnePhasethree\ & 2,504 & 6,468,094 & 131.17 & 5\\
	\ThreePhasethree\ & 2,504 & 19,381,970 & 393.06 & 5\\
	\FullPhasethree\ & 2,504 & 79,000,000 & 1602 & 5\\\botrule
\end{tabular}}{Datasets used in this study; based on portions of the Phase 1 and Phase 3 data from the 1000 genomes project.
In-memory size is the approximate memory required to store the data as a double-precision matrix of size n,m using the formula: n*m*8bytes/10\textsuperscript{9}bytes.
}
\end{table}

\begin{table*}[!t]
\processtable{Resources allocated and time taken.\label{Tab:01}}
{\begin{tabular}{ll|cc|cc|rr|c}\toprule
Tool & Dataset & \multicolumn{2}{ c |}{Preprocesing (GB)} & \multicolumn{2}{ c |}{Clustering (GB)} & \multicolumn{2}{ c |}{Time} & Accuracy\\
& & map & reduce  & map & reduce  & pre-processing & clustering & \\\midrule
        R &\NinteenPhaseone & - & - & - & - & 55m 41s & 7s &0.614\\
        Mahout & \NinteenPhaseone & 1536 & 3072 & 1536 & 3072 & 6m 10s & 8m 32s & 0.705\\
        & \OnePhaseone & 1536 & 3072 & 1536 & 3072 & 9m 52s & 12m 08s & 0.771\\
        & \SevenPhaseone & 1536 & 3072 & 4096 & 4096  & 60m 35s & 5h 44m & 0.716\\
        & \FullPhaseone & 1536 & 3072 & 6144 & 6144  & 108m 47s &  & \\
        & \OnePhasethree & 1536 & 3072 & 1536 & 3072 & 23m 27s & 21m 14s & 0.873\\
        & \ThreePhasethree & 1536 & 3072 & 2048 & 4096 & 63m 49s & 93m 18s & 0.871\\\
        & \FullPhasethree & 1536 & 3072 & 6144 & 6144 & 5h 36m & 21h 5m &0.623\\\botrule
\end{tabular}}{The resources allocated to each MapReduce yarn-container and time taken for the job(s) to complete.}
\end{table*}

>>>>

\newcommand{\OnePhaseone}{phase1\_chr1}
\newcommand{\NinteenPhaseone}{phase1\_chr19}
\newcommand{\SevenPhaseone}{phase1\_chr1-7}
\newcommand{\FullPhaseone}{phase3\_chr1-22}
\newcommand{\OnePhasethree}{phase3\_chr1}
\newcommand{\ThreePhasethree}{phase3\_chr1-3}
\newcommand{\FullPhasethree}{phase3\_chr1-22}

@@

% COMPARISON TO R
\subsection*{Clustering in Mahout requires less memory than in R}
In this section, we compare the runtime and resource requirements between the k-means clustering implementation in R and Mahout for the small \NinteenPhaseone\ dataset (see Methods). 
We measured the runtime separately for pre-processing stage as well as the clustering stage. 
With Hadoop, pre-processing the data takes approximately 6 minutes, with an allocation of up to 3GB memory per 'container'. The resulting data is stored as a Hadoop 'SequenceFile' of about 835MB in size.
Conversely,  pre-processing the data to R's in-memory matrix takes 56 minutes and required 17.7GB memory. 
K-means clustering the data, however, is faster with R, using 7s, whereas Mahout takes just under 9 minutes. See Table~\ref{datasetsTime}. \\
Due to the relatively small number of variants, cluster performance is relatively poor for both methods, with the best Adjusted Rand Index score for clustering individuals in one of 4 populations (see Methods) being 0.705 in Mahout and 0.614 in R (see Table~\ref{datasetsAcc}).

Although the overall Mahout pipeline is about 40 minutes faster than R's, Mahout's k-means clustering takes two orders of magnitude longer. 
This is likely due to the additional overhead involved in spawning the map and reduce processes, and distributing the data between nodes.
R, on the other hand, already has the entire matrix in-memory, on a single machine. This should speed up the clustering significantly as no disk-access or networking is required. However, the amount of memory available on a single machine will quickly become a limiting factor. 
% DB: very nice but how do you get to the 1.6TB ?
% AO: Fixed
As an example, the entire set of 1000 Genome Project phase3 variants could require approximately 1.6TB to be completely loaded into memory as a double-precision matrix (see Table~\ref{datasetsAcc}). This is based on the equation:
$^{n \times m \times 8bytes}/_{1GB}$, where $n \times m$ are the matrix dimensions, 8bytes is the memory a double occupies (i.e. each matrix element), and  $1GB$ is $10^9$bytes.

% DB: not clear you need to spell out your argument a bit more...
% AO: Fixed maybe
The primary benefit of Hadoop is its scalability. This is achieved through MapReduce jobs which allows the task at hand to be separated into 'containers'.
Although in the previous example, Hadoop had access to 36GB of memory distributed over 3 machines, the size of each container was only 3GB.
Each of these containers is effectively a self-contained job that is independent from any other container.
Therefore, the more resources that the user has available, the more containers that can be run in parallel, either on the same machine or separate, and in turn decreasing the run-time of the overall job.
This means that our Hadoop job can scale from a single machine with minimal resources (albeit with a longer run-time), to a huge compute cluster with terabytes of RAM.
This benefit allows Hadoop jobs to not only scale vertically, i.e. to a larger single machine as R can, but also horizontally, to a cluster of many machines.

% SCALING UP FEATURES IN MAHOUT
\subsection*{Hadoop scales to genome-wide clustering}
%DB: phase1 full genome ?
%AO: Fixed nearly
In this section we demonstrate Mahout's scaling ability by increasing the numbers of features (variants per sample) input to our algorithm to include the 79 Million variants from the entire phase3 dataset (\FullPhasethree{}).

%DB: Where is the result from \SevenPhaseone\
%AO: Fixed
We tested on various arbitrarily sized datasets to demonstrate the different container sizes required by pre-processing and clustering, as well as the time required.
On the \OnePhaseone{} dataset, pre-processing takes just under 10 minutes and clustering takes approximately 12 minutes with a container size the same as with the \NinteenPhaseone{} dataset.
We then increased the input to include the first seven chromosomes (\SevenPhaseone{}). In this case, pre-processing time increased to approximately 1 hour, and clustering to about 5 hours and 45 minutes.
Our pre-processing algorithm was successful with the same container size as the previous examples. However, we increased both the map and reduce container size for the clustering step to 4GB to accommodate the increased vector size.
Finally we used the entire phase one dataset as input. Although pre-processing now takes 108 minutes, it was again successful with the same sized containers as previously.
Clustering, however, not only required larger containers, but also took over 20 hours to complete.
This significant increase in time required is in part due to the larger container size. With each container consuming 6GB of memory, only up to six containers can run simultaneously, as opposed to 24 1.5GB containers from the smaller examples.

@@

% SCALING UP SAMPLES IN MAHOUT
\subsection*{Hadoop scales effortless to more than twice the number of samples}
In this section we investigate Mahout's ability to scale with more samples, i.e. the 2504 individuals from the phase3 dataset compared to the 1092 individuals in the phase1 dataset.
%DB: ok this makes sense from a technical point of view (how fast, memory) but you should not really discuss the accuracy ...

The container size required for pre-processing the data is identical for both datasets, with the phase3 dataset requiring less than double the time of the smaller phase1 dataset.
In this case, due to the number of Feature Vectors increasing, rather than the feature size, the memory requirements for k-means clustering should remain similar, as the cluster centres loaded into the containers' memory are approximately the same size.
This proved to be the case, as 4GB allocated per container was the minimum for both datasets. The time to complete clustering was much higher though,
especially due to the fact that only 9 4GB containers can run simultaneously, rather than the 24 1.5GB containers. 
The clustering accuracy is 0.816 for the phase1 dataset and 0.xxx for the phase3 dataset.

@@

\section*{Conclusion}
In this paper we have applied Mahout's k-means clustering to the task of clustering individuals, based on their genomic variants. 
We provide an interface from VCF format to Hadoop and Mahout, and a toolset to interpret Mahout's clustering output (see Figure 1)
We find that on small datasets the clustering stage is two orders of magnitudes slower in Mahout compared to R (9 minutes vs 7 seconds), likely due to the overhead of setting up and co-ordinating the communication between the Hadoop nodes. 
However, increasing either the number of samples or the number of features per sample quickly exceeds the capability of R on this machine due to memory limitations.
Hadoop on the other hand scales effortlessly to more than twice the number samples (2,504) and can process VCF files that contain over 79 Million variants per samples.

@@

\begin{methods}
\section{Methods}
\subsection*{Datasets}
We used variant call format (VCF) files from phases 1 and 3 of the 1000 Genomes Project.
Each VCF file details the genetic variation (SNPs and indels) for one chromosome, between each individual and a reference genome derived from GRCh37. 
The phase1 and phase3 datasets contain 1,092 and 2,504 individuals, respectively.
Metadata available from the 1000 Genomes Consortium specifies additional attributes for each individual, including population and familial data.\\
We used different subsets of the data for different comparisons. For example, to be able to compare Hadoop with R, we used the VCF file containing chromosome 19 variants (\NinteenPhaseone{}).
Then to demonstrate scaling with Hadoop, we use subsets that contain more variants, i.e. \SevenPhaseone{} and \FullPhasethree{}, which include chromosome 1-7 and the full genome, respectively.
Table~\ref{datasets} contains an overview of the datasets.

\subsection*{Hardware and Software}
We processed the data using a cluster of five VMs on the Microsoft Azure cloud service. Three of these VMs, the 'worker nodes', each have 14GB memory and and 8 CPU cores. These three VMs run the Hadoop2 NodeManager, which manages the Yet Another Resource Negotiator (YARN) 'containers'.
The user is able to specify the resources allocated to each container, where map containers can have a different allocation to reduce containers.
The fourth VM runs the HDFS NameNode, ResourceManager and monitoring services, and the fifth VM, a small, single core machine, runs the Cloudera manager service.
With a total of 42GB memory and 24 CPU cores available between the node managers, we can simultaneously run up to 24 YARN containers with 1.5GB memory per container, or 12 YARN containers with 3GB memory per container.
Storage consists of a 3TB Hadoop Distributed File System (HDFS) partition distributed across the three worker nodes. Each of these nodes runs a DataNode with a 1TB disk.

@@

We wrote two `MapReduce' classes in Java to convert VCF files to the aforementioned sequence files. This is scalable and should work on any number of files,
of any file size; limited only by disk space and time. 
The `map' stage of the first job parses each line of the VCF file to key value pairs. Each of the keys are an identical arbitrary number, where the value for each key is a sparse vector of the variants from each line. The variants in each vector are in the same order as they appear in the VCF file.
In this stage, we can define parameters to exclude certain variants that may be deemed low quality, or only appear in a certain number of individuals.
We use identical keys so that each key value pair is sent to the same reducer, and this reducer assigns a unique key to each value from the previous step. We require one reducer in this step to make each variant key a consecutive number, rather than an arbitrary feature, such as its genomic location. Because keys are represented by integers, this helps to avoid integer overflows by keeping the keys relatively small.

The second job effectively transposes the output from the first job. The mappers create key value pairs where the key is composite of the individual id and variant id, and the value is the variant.
This composite key, which is essentially a concatenation of two keys, allowed us to implement custom 'collect' and 'sort' classes to speed up the process. These classes divide up the key value pairs by their individual ID and sort them by their location ID, so each sorted collection of key/value pairs can be sent to a separate reducer.
 The reducers then write the variants for each individual to a sparse vector. These are saved to disk as the value for each individual ID key.

@@

The value is zero for independent clusterings and one for identical clusterings. 
We compared the Mahout k-means clusters and the R k-means clusters to the known clusters based on meta data from the 1000 genome project.
For the known clusters, individuals from the both phase1 and phase3 datasets were partitioned by their super population code, ASN, EUR, AFR, and AMR, where phase3 included EAS and SAS instead of ASN.

\subsection*{Performance}
We recorded the job time from the 'Elapsed' time as reported by the Hadoop JobHistory server. This is measured from the job's start time to finish time.
Because k-means clustering performs multiple iterations, and therefore spawns multiple MapReduce jobs, the time we reported is the sum of the elapsed time of each job.
For the R job, where we could not easily separate the pre-processing and clustering components, we printed the time between
stages using the function, \texttt{proc.time()}.

@@

\begin{table}[!t]
\processtable{Datasets used in this study.\label{Tab:01}}
{\begin{tabular}{lrrrrr}\toprule
& individuals & variants & in-memory size (GB) & population\\
& & & &groups& \\\midrule
        \NinteenPhaseone{} & 1,092 & 816,115 & 7.13  & 4\\
        \OnePhaseone{} & 1,092 & 3,007,196 & 26.27  & 4\\
        \SevenPhaseone{} & 1,092 & 18,984,880 & 165.85 & 4\\
	\OnePhasethree{} & 2,504 & 6,468,094 & 131.17 & 5\\
	\ThreePhasethree{} & 2,504 & 19,381,970 & 393.06 & 5\\
	\FullPhasethree{} & 2,504 & 79,000,000 & 1602 & 5\\\botrule
\end{tabular}}{Datasets used in this study; based on portions of the phase1 and phase3 data from the 1000 genomes project.
In-memory size is the approximate memory required to store the data as a double-precision matrix of size n,m using the formula: n*m*8bytes/10\textsuperscript{9}bytes.
}
\end{table}

\begin{table*}[!t]
\processtable{Resources allocated and time taken.\label{Tab:01}}
{\begin{tabular}{ll|cc|cc|rr|c}\toprule
Tool & Dataset & \multicolumn{2}{ c |}{Preprocesing (GB)} & \multicolumn{2}{ c |}{Clustering (GB)} & \multicolumn{2}{ c |}{Time} & Accuracy\\
& & map & reduce  & map & reduce  & pre-processing & clustering & \\\midrule
        R &\NinteenPhaseone{} & - & - & - & - & 55m 41s & 7s &0.614\\
        Mahout & \NinteenPhaseone{} & 1536 & 3072 & 1536 & 3072 & 6m 10s & 8m 32s & 0.705\\
        & \OnePhaseone{} & 1536 & 3072 & 1536 & 3072 & 9m 52s & 12m 08s & 0.771\\
        & \SevenPhaseone{} & 1536 & 3072 & 4096 & 4096  & 60m 35s & 5h 44m & 0.716\\
        & \FullPhaseone{} & 1536 & 3072 & 6144 & 6144  & 108m 47s &  & \\
        & \OnePhasethree{} & 1536 & 3072 & 1536 & 3072 & 23m 27s & 21m 14s & 0.873\\
        & \ThreePhasethree{} & 1536 & 3072 & 2048 & 4096 & 63m 49s & 93m 18s & 0.871\\\
        & \FullPhasethree{} & 1536 & 3072 & 6144 & 6144 & 5h 36m & 21h 5m &0.623\\\botrule
\end{tabular}}{The resources allocated to each MapReduce yarn-container and time taken for the job(s) to complete.}
\end{table*}
